---
title: "Rejection Sampling"
author: "Nathan Cheung"
date: "`December 7, 2018`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ProbabilityProject)
```

## Rejection Sampling
Rejection Sampling assumes that a random variable, X, has pdf f(x) such that 
  1)f(x) <= C
  2)There exists a,b such that P(a<=x<=b) = 1
  
Then, we let u=uniform(a,b) and v=uniform(0,C)
  We accept U as a sample from our pdf if v <= f(u)
  We reject U as a sample from our pdf if v > f(u)

## Description
rejectionsample takes a random sample of length n of the given pdf

## Usage
``` {r}
pdf <- function(x){
 dbeta(x,3,2)
}

rejectionsample(n, pdf, a, b, C)
```
## Arguments
n     the number of samples

pdf   a function that is the pdf of the random             variable you wish to sample from 

a     a numeric that is the lower bound of the random
      variable you wish to sample from
      
b     a numeric that is the upper bound of the random       variable you wish to sample from

C     a numeric that is such that f(x) <= C for all
      values of x

## Note
pdf is a function that must be made before running rejectionsample

Use pdf <- function(x){
    
    }
    
Specify the parameters of the random variable in the pdf function (see examples)

## Examples
1)
```{r}
pdf <- function(x){
  dbeta(x,3,2)
  }
  
  rejectionsample(10000, pdf, 0, 1, 2)
```  
  
2)
```{r}
pdf <- function(x){
  dgamma(x,2,1)
  }
  
  rejectionsample(5000,pdf,0,5,3)
```
